---
title: "Report on potential inequality in prison system"
author: "Zerong Wang"
date: '2022-11-01'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
One of the sharpest manifestations of racism in the United States is its prison system. In this report, I will use incarceration data collected by the Vera Institute to expose patterns of inequality. I will present a brief analysis of a dataset of trends in incarceration in the United States and use the data and calculations from the dataset to provide visualizations as evidence of patterns of inequality in the exposed prison system.

## Introduction


## Data summary

## Growth of the U.S. Prison Population
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_for_us()
```
This above chart shows the trend in the growth of the U.S. jail population over time.

##  Growth of Prison Population by State 
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_by_states(c("WA", "OR", "CA"))
```
In the chart above, it shows the trend in the growth of the prison populations of California, Washington, and 
Oregon over time. 

## Comparison urbanicity inequality 
Do some kinds of counties seem to imprison more people than other kinds of counties? 
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_by_urbanicity(c("rural", "small/mid", "suburban", "urban"))
```

## Map
```{r, echo=FALSE, eval=TRUE}
cases_map
```