---
title: "Report on racism in prison system"
author: "Zerong Wang"
date: '2022-11-01'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
[TODO: Include a short abstract (about 50 words)]

## Introduction


## Data summary

## Growth of the U.S. Prison Population
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_for_us()
```
This above chart shows the trend in the growth of the U.S. jail population over time.

##  Growth of Prison Population by State 
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_by_states(c("WA", "OR", "CA"))
```
In the chart above, it shows the trend in the growth of the prison populations of California, Washington, and 
Oregon over time. 

## Comparison inequality 
Do some kinds of counties seem to imprison more people than other kinds of counties? 
```{r, echo=FALSE, eval=TRUE}
plot_jail_pop_by_urbanicity(c("rural", "small/mid", "suburban", "urban"))
```


## Map 
* Here's another test. A vector
of numbers: `r test_query2(num)`.
